\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-02-23 trunk/europa-basics.tex
heading changes based on Minh and discussion; also noted FP comments

\subsection{Automated Planning and \eu}
\label{sec:planningfound}

@@

\paragraph \textit{Planning}: The Shopping Agent Problem
\cite{russelnorvig} is a variation of the problem with which we started this chapter.
In this problem, an agent needs to purchase a set of products
(milk, drill, etc) that are available at specific locations
(supermarket, hardware store, etc) and the agent is subject to
temporal (must complete tasks by specific deadlines) and resource
(fuel, carrying capacity, etc) constraints. The agent needs to figure
out what actions need to be performed to find and acquire the required
items, as well as when to perform each of those
actions. Fig. \ref{fig:shopping-1} shows a solution produced by \eu
for such a problem instance.

>>>>

\subsection{Automated Planning}
\label{sec:planningfound}

@@

\paragraph{} \textit{Planning}: The Shopping Agent Problem
\cite{russelnorvig} is a variation of the problem with which we
started this chapter.  In this problem, an agent needs to purchase a
set of products (milk, drill, etc) that are available at specific
locations (supermarket, hardware store, etc). The agent is subject to
temporal (must complete tasks by specific deadlines) and resource
(fuel, carrying capacity, etc) constraints and it needs to synthesize
actions that need to be performed to find and acquire the required
items, as well as when to perform each of those actions.
Fig. \ref{fig:shopping-1} shows a solution produced by \eu for such a
problem instance.
